\textbf{INSERT TITLE HERE}

### 2013-11-16 LaTeX/paper.tex
Ray fucked up

\section{Assumptions and Justifications}

>>>>

\section{Assumptions and Justifications}
\begin{enumerate}
    \item The travel times given are calculated from an optimal route from the center of the first
        zone to the center of ths econd. This excludes the possibility of reaching a zone faster
        via an indirect route from the direct, given one.
    \item The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item
        Overlap of ambulance coverage in a zone will be treated as even coverage over the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, due to
        ambulances  %TODO
